My title

### 2023-03-15 outputs/paper/paper.qmd
Removed the variables "degree", "income", and "rincome" from our entire analysis as we chose not to focus on them in our final analysis.

## import averaged variable datasets 
mean_age <- read.csv(here::here("outputs/data/mean_age.csv"))
mean_edu <- read.csv(here::here("outputs/data/mean_edu.csv"))
mean_happy <- read.csv(here::here("outputs/data/mean_happy.csv"))
mean_income <- read.csv(here::here("outputs/data/mean_income.csv"))
mean_marital <- read.csv(here::here("outputs/data/mean_marital.csv"))
mean_race <- read.csv(here::here("outputs/data/mean_race.csv"))
mean_sex <- read.csv(here::here("outputs/data/mean_sex.csv"))
mean_childs <- read.csv(here::here("outputs/data/mean_childs.csv"))

@@

@@

```{r}
#| echo: false
# ATTEMPT: Summary statistics of our GSS data 
# summ_gss <- cleaned_2016gss_data %>% 
#   select(age, sex, race, income, rincome, 
#          degree, childs, marital,
#          happy, wwwhr)
# sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
## the final line doesn't work for some reason and i'm mad

# Table showing the first 10 rows of our cleaned dataset
cleaned_2016gss_data |> 
  select(age, sex, race, 
         degree, childs, marital,
         happy, wwwhr) |> 
  slice(1:8) |> 
  kable(caption='A subset of key features',
        col.names = c("Age", "Sex", "Race", "Highest Degree", 
                      "Number of Children", "Marital Status", "Happiness Level", 
                      "Weekly Internet Hours"),
        digits = 1,
        booktabs = FALSE,
        linesep = "") |>
  kable_styling(full_width = T)
```

@@

```{r}
#| label: fig-personalincomeandinternet
#| fig-cap: Average Weekly Total of Internet Use by Personal Income
#| echo: false

# personal income
cleaned_2016gss_data |>
  ggplot(mapping = aes(x = factor(income, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '9', '10', '11', '$25,000+', 'NA')))) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  labs(x = "Personal Income", y = "Number of Respondents")

Max - might emit...

```{r}
#| label: fig-familyincomeandinternet
#| fig-cap: Average Weekly Total of Internet Use by Family Income
#| echo: false

# use tidyverse-style code to pivot and summarise the data 
mean_income |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Average Total Family Income",
    y = "Internet Usage Hours"
  )

# total family income
cleaned_2016gss_data |>
  ggplot(mapping = aes(x = factor(rincome, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '$10,000 to $14,999', '$15,000 to $19,999', '$20,000 to $24,999', '$25,000+', 'NA')))) +
  geom_bar() +
  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
  labs(x = "Total Family Income", y = "Number of Respondents")

Max - might emit

@@

```{r}
#| label: fig-degreeandinternet
#| fig-cap: Weekly Total of Internet Use by Highest Education Obtained
#| echo: false

# use tidyverse-style code to pivot and summarise the data 
mean_edu |> ggplot(aes(x = variable, y = value)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Highest Education Obtained",
    y = "Internet Usage Hours"
  )
```

@fig-degreeandinternet displays the relationship between highest level of education obtained by the respondent and internet usage in 2016. Those who have completed a less than high school degree use the internet the least.

>>>>

## import averaged variable datasets 
mean_age <- read.csv(here::here("outputs/data/mean_age.csv"))
mean_happy <- read.csv(here::here("outputs/data/mean_happy.csv"))
mean_marital <- read.csv(here::here("outputs/data/mean_marital.csv"))
mean_race <- read.csv(here::here("outputs/data/mean_race.csv"))
mean_sex <- read.csv(here::here("outputs/data/mean_sex.csv"))
mean_childs <- read.csv(here::here("outputs/data/mean_childs.csv"))

@@

Saku :) :)

@@

```{r}
#| echo: false
# Table showing the first 10 rows of our cleaned dataset
cleaned_2016gss_data |> 
  select(wwwhr, age, sex, race, 
         degree, childs, marital,
         happy) |> 
  slice(1:8) |> 
  kable(caption='A subset of key features',
        col.names = c("Weekly Internet Hours", "Age", "Sex", "Race", "Highest Degree", 
                      "Number of Children", "Marital Status", "Happiness Level"),
        digits = 1,
        booktabs = FALSE,
        linesep = "") |>
  kable_styling(full_width = T)
```

@@

@@
